Continuous developmental changes in word recognition support language learning across early childhood

### 2025-04-03 paper/paper.Rmd
author affil tweak

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Michael C. Frank
    affiliation: a, 1
  - name: Virginia A. Marchman
    affiliation: a
  - name: Claire Augusta Bergey
    affiliation: b
  - name: Veronica Boyce
    affiliation: a
  - name: Mika Braginsky
    affiliation: a
  - name: George Kachergis
    affiliation: a
  - name: Jess Mankewitz
    affiliation: c
  - name: Stephan Meylan
    affiliation: d
  - name: Ben Prystawski
    affiliation: a
  - name: Nilam Ram
    affiliation: a, e
  - name: Robert Z. Sparks
    affiliation: a
  - name: Adrian Steffan
    affiliation: f
  - name: Alvin Wei Ming Tan
    affiliation: a
  - name: Martin Zettersten
    affiliation: f
address:
  - code: a
    address: Department of Psychology, Stanford University, Stanford, CA, USA
  - code: b
    address: Department of Linguistics, Stanford University, Stanford, CA, USA
  - code: c
    address: Department of Psychology, University of Wisconsin, Madison, WI, USA
  - code: d
    address: Department of Linguistics, University of California, Berkeley, CA, USA
  - code: e
    address: Department of Communication, Stanford University, Stanford, CA, USA
  - code: f
    address: Department of Communication, Stanford University, Stanford, CA, USA
  - code: g
    address: Department of Psychology, Ludwig Maximilian University, Munich, Germany

>>>>

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Michael C. Frank
    affiliation: a, 1
  - name: Virginia A. Marchman
    affiliation: a
  - name: Claire Augusta Bergey
    affiliation: b
  - name: Veronica Boyce
    affiliation: a
  - name: Mika Braginsky
    affiliation: a
  - name: George Kachergis
    affiliation: a
  - name: Jess Mankewitz
    affiliation: c
  - name: Stephan Meylan
    affiliation: d
  - name: Ben Prystawski
    affiliation: a
  - name: Nilam Ram
    affiliation: a, e
  - name: Robert Z. Sparks
    affiliation: a
  - name: Adrian Steffan
    affiliation: f
  - name: Alvin Wei Ming Tan
    affiliation: a
  - name: Martin Zettersten
    affiliation: g
address:
  - code: a
    address: Department of Psychology, Stanford University, Stanford, CA, USA
  - code: b
    address: Department of Linguistics, Stanford University, Stanford, CA, USA
  - code: c
    address: Department of Psychology, University of Wisconsin, Madison, WI, USA
  - code: d
    address: Department of Linguistics, University of California, Berkeley, CA, USA
  - code: e
    address: Department of Communication, Stanford University, Stanford, CA, USA
  - code: f
    address: Department of Psychology, Ludwig Maximilian University, Munich, Germany
  - code: g
    address: Department of Cognitive Science, University of California, San Diego, CA, USA
